---
title: "DYNECOM EDA synchrony"
author: "Ben Cowley"
date: "10 March 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/home/bcowley/Benslab/METHODMAN/project_DYNECOM/')
library(tidyverse)
library(reshape2)
library(RcppRoll)
library(DAAG)
library(cocor)
library(gghalves)
source('sync_functions.R')
source('znbnz_utils.R')
```

# PARAMETERS

```{r params}
# data-type parameters
basepath <- 'EDAcsv'
feature <- 'scr'
centr <- TRUE
skale <- TRUE
# List of conditions
paircond <- c('a', 'b')
dyadcond <- c('D', 'S')
physcond <- c('both', 'eeg', 'resp', 'na')
timecond <- c('BL', '30s', '6min')
# sliding window parameters
wndw <- 40
step <- wndw / 2 # 50% overlap steps
method <- "sd" # options are: max, mean, median, min, prod, sd, sum, var; see ?RcppRoll
REPS <- 10000
```

# CODE WRANGLING

Here, as an example, we select condition *D, both, 6min*
We collect _a_ and _b_ versions of the data (which are then bound together for convenience)

```{r wrangle}
# Create the first dataset as an example
cond_str <- paste0('_', dyadcond[1], '_', physcond[1], '.*', timecond[3])
dfa <- read_all_recordings(basepath, pat=paste0(paircond[1], cond_str), ext="csv", skip = 1)
dfb <- read_all_recordings(basepath, pat=paste0(paircond[2], cond_str), ext="csv", skip = 1)
dfa$ab <- 1
dfb$ab <- 2
df <- rbind(dfa, dfb)

subjs <- unique(df$Part)
sbjix <- seq(1, length(subjs))
```


# SLIDING WINDOW CORRELATIONS

Within each dyad, a statistic is taken within sliding windows, for each signal, _a_ and _b_. The statistic is chosen in the 'method' parameter above, and should reflect the aspect of physiology we believe is synchronizing. Then, the Pearson correlation coefficient is obtained. This is extended to the combination of all with all, to obtain the correlation matrix displayed.

The diagonal of the matrix (true dyad correlations) provides the test measurement. The diagonal is averaged (correlation aggregation is not needed because the number of elements per correlation is constant across dyads).

```{r sldgwndw}
Db6m.pr1.1 <- corr_rollme_1pr(df, 1, 1, feature, wndw, step, CTR = centr, SCL = skale)
# Db6m.corr <- corr_rollme_allpr(df, feature, wndw, step)

Db6m.cormat <- corr_rollme_mat(df, feature, wndw, step, method, CTR = centr, SCL = skale)
Db6m.corr <- diag(Db6m.cormat$corr)
# Db6m.count <- Db6m.cormat$count

# Aggregates
Db6m.avg.cor <- mean(Db6m.corr)   # for constant N, Hunter-Schmidt aggregation is equivalent to average correlation
Db6m.abav.cor <- mean(abs(Db6m.corr)) # for constant N, Hunter-Schmidt aggregation is equivalent to average correlation

# show corr matrix
plot_rwb_cormat(Db6m.cormat$corr)

```


# MATRIX SAMPLING

To obtain a random sample (without replacement) of the pair-wise correlations, we simply shuffle the columns of the correlation matrix, displayed.

```{r matrix-sampling}
samp <- sample_matrix(Db6m.cormat$corr, repl = FALSE)
plot_rwb_cormat(samp$sampmat)
```


# PERMUTATION TESTING

To obtain a permutation test statistic, we repeat the random sampling 10000 times, generating a distribution of correlations. We plot the observed real correlation against the distribution to see the statistical difference of the obervation from a random distribution. P values are obtained by counting how many permuted mean-differences are larger than the one we observed in our actual data. We can then divide this by the number of items in our permutation distribution.

```{r permutation}
# CONDITION D_both_6mins
Db.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, Db6m.cormat$corr))
hist(Db.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(Db.obsVrand_corr) > abs(Db6m.avg.cor)) / REPS))
abline(v=Db6m.avg.cor, col='blue', lwd=2)
```


## OTHER DYADIC CONDITIONS


```{r enumconds}
# CONDITION D_eeg_6mins
cond_str <- paste0(dyadcond[1], '_', physcond[2], '.*', timecond[3])
patts <- c(paste0(paircond[1], '_', cond_str), paste0(paircond[2], '_', cond_str))
De6m.cor <- cond2rollcormat(basepath, patts, feature, wndw, step, method, triangle = FALSE, CTR = centr, SCL = skale)
# Permutation testing
De.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, De6m.cor$cormat))
hist(De.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(De.obsVrand_corr) > abs(De6m.cor$avg.cor)) / REPS))
abline(v=De6m.cor$avg.cor, col='blue', lwd=2)



# CONDITION D_resp_6mins
cond_str <- paste0(dyadcond[1], '_', physcond[3], '.*', timecond[3])
patts <- c(paste0(paircond[1], '_', cond_str), paste0(paircond[2], '_', cond_str))
Dr6m.cor <- cond2rollcormat(basepath, patts, feature, wndw, step, method, triangle = FALSE, CTR = centr, SCL = skale)
# Permutation testing
Dr.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, Dr6m.cor$cormat))
hist(Dr.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(Dr.obsVrand_corr) > abs(Dr6m.cor$avg.cor)) / REPS))
abline(v=Dr6m.cor$avg.cor, col='blue', lwd=2)



# CONDITION D_na_6mins
cond_str <- paste0(dyadcond[1], '_', physcond[4], '.*', timecond[3])
patts <- c(paste0(paircond[1], '_', cond_str), paste0(paircond[2], '_', cond_str))
Dn6m.cor <- cond2rollcormat(basepath, patts, feature, wndw, step, method, triangle = FALSE, CTR = centr, SCL = skale)
# Permutation testing
Dn.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, Dn6m.cor$cormat))
hist(Dn.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(Dn.obsVrand_corr) > abs(Dn6m.cor$avg.cor)) / REPS))
abline(v=Dn6m.cor$avg.cor, col='blue', lwd=2)
```

## ALL SOLO CONDITIONS


```{r soloconds}
# CONDITION S_both_6mins
cond_str <- paste0(dyadcond[2], '_', physcond[1], '.*', timecond[3])
patts <- c(paste0(paircond[1], '_', cond_str), paste0(paircond[2], '_', cond_str))
Sb6m.cor <- cond2rollcormat(basepath, patts, feature, wndw, step, method, triangle = FALSE, CTR = centr, SCL = skale)
# Permutation testing
Sb.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, Sb6m.cor$cormat))
hist(Sb.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(Sb.obsVrand_corr) > abs(Sb6m.cor$avg.cor)) / REPS))
abline(v=Sb6m.cor$avg.cor, col='blue', lwd=2)


# CONDITION S_eeg_6mins
cond_str <- paste0(dyadcond[2], '_', physcond[2], '.*', timecond[3])
patts <- c(paste0(paircond[1], '_', cond_str), paste0(paircond[2], '_', cond_str))
Se6m.cor <- cond2rollcormat(basepath, patts, feature, wndw, step, method, triangle = FALSE, CTR = centr, SCL = skale)
# Permutation testing
Se.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, Se6m.cor$cormat))
hist(Se.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(Se.obsVrand_corr) > abs(Se6m.cor$avg.cor)) / REPS))
abline(v=Se6m.cor$avg.cor, col='blue', lwd=2)


# CONDITION S_resp_6mins
cond_str <- paste0(dyadcond[2], '_', physcond[3], '.*', timecond[3])
patts <- c(paste0(paircond[1], '_', cond_str), paste0(paircond[2], '_', cond_str))
Sr6m.cor <- cond2rollcormat(basepath, patts, feature, wndw, step, method, triangle = FALSE, CTR = centr, SCL = skale)
# Permutation testing
Sr.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, Sr6m.cor$cormat))
hist(Sr.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(Sr.obsVrand_corr) > abs(Sr6m.cor$avg.cor)) / REPS))
abline(v=Sr6m.cor$avg.cor, col='blue', lwd=2)


# CONDITION S_na_6mins
cond_str <- paste0(dyadcond[2], '_', physcond[4], '.*', timecond[3])
patts <- c(paste0(paircond[1], '_', cond_str), paste0(paircond[2], '_', cond_str))
Sn6m.cor <- cond2rollcormat(basepath, patts, feature, wndw, step, method, triangle = FALSE, CTR = centr, SCL = skale)
# Permutation testing
Sn.obsVrand_corr <- replicate(REPS, sampmat_diag_stat(mean, Sn6m.cor$cormat))
hist(Sn.obsVrand_corr, col='black', breaks=100, 
     main = paste(cond_str, ", two-tailed p =", sum(abs(Sn.obsVrand_corr) > abs(Sn6m.cor$avg.cor)) / REPS))
abline(v=Sn6m.cor$avg.cor, col='blue', lwd=2)
```


```{r plotSync}
df.sync <- data.frame("D_na" = Dn6m.cor$avg.cor, "D_eeg" = De6m.cor$avg.cor, 
                      "D_resp" = Dr6m.cor$avg.cor, "D_both" = Db6m.avg.cor, 
                      "S_na" = Sn6m.cor$avg.cor, "S_eeg" = Se6m.cor$avg.cor, 
                      "S_resp" = Sr6m.cor$avg.cor, "S_both" = Sb6m.cor$avg.cor) %>% 
        gather(key = "Condition", value = "synchrony")
df.perm <- data.frame("D_na" = Dn.obsVrand_corr, "D_eeg" = De.obsVrand_corr, 
                      "D_resp" = Dr.obsVrand_corr, "D_both" = Db.obsVrand_corr, 
                      "S_na" = Sn.obsVrand_corr, "S_eeg" = Se.obsVrand_corr, 
                      "S_resp" = Sr.obsVrand_corr, "S_both" = Sb.obsVrand_corr) %>% 
        gather(key = "Condition", value = "synchrony") %>%
        mutate(Condition=factor(Condition, levels=rev(df.sync$Condition)))

# Basic violin plot
ggplot(df.perm, aes(x=Condition, y=synchrony)) + 
        geom_half_violin(trim=FALSE, fill="gray", side = "r") +
        geom_boxplot(width=0.1, outlier.shape = NA) +
        geom_crossbar(aes(ymin = synchrony, ymax = synchrony), df.sync, color = "red") +
        coord_flip() +
  labs(title="Permutation test of SCR synchrony per condition", x="Condition", y = "Synchrony (correlation)") +
  theme_classic()
```

## RELATION TO SELF-REPORTS

Read Simo's csv file and create linear regression on S.na synchrony data

```{r selfrep}
df <- read.csv('dynecom_Data.csv')

# DEALING WITH THE EDA RESULT CONDITION FIRST
df.Sna.a <- df %>% filter(Scenario == 5 & AorB == 1)
df.Sna.a$sync <- Sn6m.cor$corrs
df.Sna.b <- df %>% filter(Scenario == 5 & AorB == 2)
df.Sna.b$sync <- Sn6m.cor$corrs
df.Sna <- rbind(df.Sna.a, df.Sna.b)

df.Sna.mdl <- lm(sync ~ Batson_empathy + 
                         inter_arousal + inter_dominance + inter_valence + interCP + interPAI + interPAU +
                         SAM_Arousal_self + SAM_Valence_self + SAM_Dominance_self + 
                         Co_Presence_self + 
                         Perceived_Affective_Interdependence_self + Perceived_Affective_Understanding_self +
                         Relationship_legth_mean + Closeness_mean + Sex, data = df.Sna)
summary(df.Sna.mdl)


with(df.Sna, plot(jitter(sync, 2), jitter(interCP, 2)))
with(df.Sna, plot(jitter(sync, 2), jitter(interPAU, 2)))
with(df.Sna, plot(jitter(sync, 2), Sex))
# Sex violin plot
ggplot(df.Sna, aes(x=as.factor(Sex), y=sync)) + 
        geom_half_violin(trim=FALSE, fill="gray", side = "r") +
        geom_boxplot(width=0.1, outlier.shape = NA) +
        labs(title="SCR synchrony per gender", x="Gender", y = "Synchrony (correlation)") +
        coord_flip() +
        theme_classic()
```


## DIFFERENCE OF CONDITIONS

Check the statistical significance of difference in synchrony between conditions. We do this by subtracting correlation vector of one condition from the other condition, then performing one-sample t-test and permutation test of difference from zero. We take the subtraction in the direction of our hypothesis of which is greater: for example, we expect synchrony to be higher in Dyad than Solo condition, so we test (Dyad - Solo).

```{r compareCond}
# idx <- intersect(subjs, )
DSboth <- Db6m.corr - Sb6m.cor$corrs
t.test(DSboth)
onet.permutation(DSboth)

# DSeeg <- De6m.cor$corrs - Se6m.cor$corrs
# t.test(DSeeg)
# onet.permutation(DSeeg)
# 
# DSresp <- Dr6m.cor$corrs - Sr6m.cor$corrs
# t.test(DSresp)
# onet.permutation(DSresp)

DSnone <- Dn6m.cor$corrs - Sn6m.cor$corrs
t.test(DSnone)
onet.permutation(DSnone)
```
